\pkg{DNest4}: An implementation of Diffusive Nested Sampling in C++11 and Python

### 2016-05-10 paper/ms.tex
JSS stuff

\documentclass[a4paper, 12pt]{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{dsfont}
\usepackage{minted}
\usepackage[left=2cm, right=2cm, bottom=3cm, top=2cm]{geometry}

@@

\title{DNest4: An implementation of Diffusive Nested Sampling
in C++11 and Python}
\author{Brendon J. Brewer\\
Dan Foreman-Mackey}
\date{}

@@

\subsection{Diffusive Nested Sampling}

\section{Basic usage of DNest4}

\section{Advanced usage}

\subsection{Multithreading}

\section{Implementing models}

\subsection{Implementing models via {\tt generate.py}}

\section{Python package}

% Assign to DFM

\section{Examples}
% Reasonably simple examples

@@

\subsection{}

>>>>

\documentclass[article]{jss}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{dsfont}
\usepackage{minted}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% declarations for jss.cls %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% almost as usual
\author{Brendon J. Brewer\\The University of Auckland\And 
        Dan Foreman-Mackey\\Washington}
\title{\pkg{DNest4}: An implementation of Diffusive Nested Sampling in
C++11 and Python}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Brendon J. Brewer, Dan Foreman-Mackey} %% comma-separated
\Plaintitle{A Capitalized Title: Something about a Package foo} %% without formatting
\Shorttitle{\pkg{foo}: A Capitalized Title} %% a short title (if necessary)

%% an abstract and keywords
\Abstract{DNest4 is good.}

\Keywords{keywords, comma-separated, not capitalized, \proglang{C++11},
\proglang{Python}}
\Plainkeywords{keywords, comma-separated, not capitalized, Java} %% without formatting
%% at least one keyword must be supplied

%% publication information
%% NOTE: Typically, this can be left commented and will be filled out by the technical editor
%% \Volume{50}
%% \Issue{9}
%% \Month{June}
%% \Year{2012}
%% \Submitdate{2012-06-04}
%% \Acceptdate{2012-06-04}

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Brendon J. Brewer\\
  Department of Statistics\\
  The University of Auckland\\
  Private Bag 92019\\
  Auckland, 1142\\
  New Zealand\\
  E-mail: \email{bj.brewer@auckland.ac.nz}\\
  URL: \url{https://www.stat.auckland.ac.nz/~brewer/}
}

@@

@@

%\subsection{Diffusive Nested Sampling}

%\section{Basic usage of DNest4}

%\section{Advanced usage}

%\subsection{Multithreading}

%\section{Implementing models}

%%\subsection{generate}

%\section{Python package}

%% Assign to DFM

%\section{Examples}
% Reasonably simple examples

@@
